When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-12-13 doc/agu_2017/vpd.tex
slides looking very good, ready for walkthough

\usepackage[english]{babel}
\usepackage[export]{adjustbox}
 % \usepackage[utf8x]{inputenc}
\usepackage[style=authoryear]{biblatex}
\addbibresource{references.bib}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{relsize}
\usepackage[absolute,overlay]{textpos}
\graphicspath{{figures/}}
\DeclareMathOperator{\sign}{sign}

@@

\section{Results - theory}
\begin{frame}{Consequences of theory - ``sign'' term}
  \[\frac{\partial \, ET}{\partial \, VPD} = \text{scaling} \cdot \left(\frac{\textcolor{magenta}{\boldsymbol{ c_p}}}{R_{air}} - \frac{\gamma c_s }{1.6 \; \textcolor{magenta}{\boldsymbol{R*}}\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{VPD}}{2 (g_1 + \sqrt{VPD})^2}\right) \right)\]
  \begin{itemize}
  \item $\textcolor{magenta}{\boldsymbol{c_p}}$ and $\textcolor{magenta}{\boldsymbol{R*}}$ are constants
  \end{itemize}
\end{frame}

\begin{frame}{Consequences of theory - ``sign'' term}
  \[\frac{\partial \, ET}{\partial \, VPD} = \text{scaling} \cdot \left(\frac{ c_p}{\textcolor{magenta}{\boldsymbol{R_{air}}}} - \frac{\textcolor{magenta}{\boldsymbol{\gamma}} \textcolor{magenta}{\boldsymbol{c_s}} }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{VPD}}{2 (g_1 + \sqrt{VPD})^2}\right) \right)\]
  \begin{itemize}
  \item $c_p$ and $R*$ are constants
  \item $\textcolor{magenta}{\boldsymbol{R_{air}}}$, $\textcolor{magenta}{\boldsymbol{\gamma}}$, and $\textcolor{magenta}{\boldsymbol{c_s}}$ are approximately constant (relative to $\sqrt{VPD}$)
  \end{itemize}
\end{frame}

\begin{frame}{Consequences of theory - ``sign'' term}
  \[\frac{\partial \, ET}{\partial \, VPD} = \text{scaling} \cdot \left(\frac{ c_p}{R_{air}} - \frac{\gamma c_s }{1.6 \; R*\; \text{ \textcolor{magenta}{\textbf{uWUE }}}} \left( \frac{2 \textcolor{magenta}{\boldsymbol{g1}} + \sqrt{VPD}}{2 (\textcolor{magenta}{\boldsymbol{g1}} + \sqrt{VPD})^2}\right) \right)\]
  \begin{itemize}
  \item $c_p$ and $R*$ are constants
  \item $R_{air}$, $\gamma$, and $c_s$ are approximately constant (relative to $\sqrt{VPD}$)
  \item \textcolor{magenta}{\textbf{uWUE}} and $\textcolor{magenta}{\boldsymbol{g1}}$ are constants within plant type (e.g. grass, crops, deciduous broadleaf forest, evergreen needleleaf forest, shrub)
  \end{itemize}
  So within each plant type, whether the atmospheric demand (ET increasing with VPD) or plant response (ET decreasing with VPD) dominates is essentially just a function of VPD!
\end{frame}

\begin{frame}{Consequences of theory - ``sign'' term}
  \[\frac{\partial \, ET}{\partial \, VPD} = \text{scaling} \cdot \left(\frac{ c_p}{R_{air}} - \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g1 + \sqrt{VPD}}{2 (g1 + \sqrt{VPD})^2}\right) \right)\]
  \begin{itemize}
  \item $c_p$ and $R*$ are constants
  \item $R_{air}$, $\gamma$, and $c_s$ are approximately constant (relative to $\sqrt{VPD}$)
  \item uWUE and $g1$ are constants within plant type (e.g. grass, crops, deciduous broadleaf forest, evergreen needleleaf forest, shrub)
  \end{itemize}
  So \textbf{within each plant type}, whether the atmospheric demand (ET increasing with VPD) or plant response (ET decreasing with VPD) dominates is approximately \textbf{just a function of VPD}!
\end{frame}

@@

\begin{frame}{Test theory with FLUXNET data - the good}
  \begin{columns}
    \begin{column}{0.33\textwidth}
      \includegraphics[width=1.2\textwidth]{DBF_box.pdf}
    \end{column}
    \begin{column}{0.33\textwidth}
    \end{column}
    \begin{column}{0.33\textwidth}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Test theory with FLUXNET data - the good}
  \begin{columns}
    \begin{column}{0.33\textwidth}
      \includegraphics[width=1.2\textwidth]{DBF_box.pdf}
    \end{column}
    \begin{column}{0.33\textwidth}
      \includegraphics[width=1.2\textwidth]{ENF_box.pdf}
    \end{column}
    \begin{column}{0.33\textwidth}
      \includegraphics[width=1.2\textwidth]{CSH_box.pdf}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Test theory with FLUXNET data - the bad}
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{GRA_box.pdf}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{CRO_box.pdf}
    \end{column}
  \end{columns}
\end{frame}

@@

\section{References}
\begin{frame}{References}
  \AtNextBibliography{\small}
  \printbibliography
  \scriptsize
  \begin{itemize}
  \item This work used eddy covariance data acquired and shared by the FLUXNET community, including these networks: AmeriFlux, AfriFlux, AsiaFlux, CarboAfrica, CarboEuropeIP, CarboItaly, CarboMont, ChinaFlux, Fluxnet-Canada, GreenGrass, ICOS, KoFlux, LBA, NECC, OzFlux-TERN, TCOS-Siberia, and USCCC. The ERA-Interim reanalysis data are provided by ECMWF and processed by LSCE. The FLUXNET eddy covariance data processing and harmonization was carried out by the European Fluxes Database Cluster, AmeriFlux Management Project, and Fluxdata project of FLUXNET, with the support of CDIAC and ICOS Ecosystem Thematic Center, and the OzFlux, ChinaFlux and AsiaFlux offices.
    \item This material is based upon work supported by the National Science Foundation Graduate Research Fellowship under Grant No. DGE 16-44869. Any opinion, findings, and conclusions or recommendations expressed in this material are those of the authors(s) and do not necessarily reflect the views of the National Science Foundation.
    \end{itemize}
\end{frame}

@@

>>>>

\usepackage[english]{babel}
\usepackage[export]{adjustbox}
% \usepackage[utf8x]{inputenc}
\usepackage[style=authoryear]{biblatex}
\addbibresource{references.bib}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{relsize}
\usepackage{textcomp}
\usepackage[absolute,overlay]{textpos}
\graphicspath{{figures/}}
\DeclareMathOperator{\sign}{sign}

@@

\section{Results - theory}
\begin{frame}{Consequences of theory - ``sign'' term}
  \[\frac{\partial \, ET}{\partial \, VPD} = \text{scaling} \cdot \left(\frac{\textcolor{magenta}{\boldsymbol{ c_p}}}{R_{air}} - \frac{\gamma c_s }{1.6 \; \textcolor{magenta}{\boldsymbol{R*}}\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{VPD}}{2 (g_1 + \sqrt{VPD})^2}\right) \right)\]
  \begin{overprint}
    \onslide<1>
    \begin{itemize}
    \item $\textcolor{magenta}{\boldsymbol{c_p}}$ and $\textcolor{magenta}{\boldsymbol{R*}}$ are constants
    \end{itemize}
    \onslide<2>
    \begin{itemize}
    \item $c_p$ and $R*$ are constants
    \item $\textcolor{magenta}{\boldsymbol{R_{air}}}$, $\textcolor{magenta}{\boldsymbol{\gamma}}$, and $\textcolor{magenta}{\boldsymbol{c_s}}$ are approximately constant (relative to $\sqrt{VPD}$)
    \end{itemize}
    \onslide<3>
    \begin{itemize}
    \item $c_p$ and $R*$ are constants
    \item $R_{air}$, $\gamma$, and $c_s$ are approximately constant (relative to $\sqrt{VPD}$)
    \item \textcolor{magenta}{\textbf{uWUE}} and $\textcolor{magenta}{\boldsymbol{g1}}$ are constants within plant type (e.g. grass, crops, deciduous broadleaf forest, evergreen needleleaf forest, shrub)
    \end{itemize}
    \onslide<4>
    \begin{itemize}
    \item $c_p$ and $R*$ are constants
    \item $R_{air}$, $\gamma$, and $c_s$ are approximately constant (relative to $\sqrt{VPD}$)
    \item uWUE and $g1$ are constants within plant type (e.g. grass, crops, deciduous broadleaf forest, evergreen needleleaf forest, shrub)
    \end{itemize}
    So \textbf{within each plant type}, whether the atmospheric demand (ET increasing with VPD) or plant response (ET decreasing with VPD) dominates is approximately \textbf{just a function of VPD}!
  \end{overprint}    
\end{frame}

@@

\begin{frame}{Test theory with FLUXNET data - the good}
    \begin{textblock*}{1.0\textwidth}(0.3\textwidth,0.8\textheight)
      \textcolor{blue}{Blue line} is theory's critical VPD.\\
  \end{textblock*}

  \begin{columns}
    \begin{column}{0.33\textwidth}<1-2>
      \includegraphics[width=1.2\textwidth]{DBF_box.pdf}
    \end{column}
    \begin{column}{0.33\textwidth}<2>
      \includegraphics[width=1.2\textwidth]{ENF_box.pdf}
    \end{column}
    \begin{column}{0.33\textwidth}<2>
      \includegraphics[width=1.2\textwidth]{CSH_box.pdf}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Test theory with FLUXNET data - the bad}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{GRA_box.pdf}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{CRO_box.pdf}
    \end{column}
  \end{columns}
      \begin{textblock*}{1.0\textwidth}(0.3\textwidth,0.85\textheight)
      \textcolor{blue}{Blue line} is theory's critical VPD.\\
  \end{textblock*}

@@

\section{References}
\begin{frame}{Acknowledgements - Thank you NSF and FLUXNET!!!}
 This work used eddy covariance data acquired and shared by the FLUXNET community, including these networks: AmeriFlux, AfriFlux, AsiaFlux, CarboAfrica, CarboEuropeIP, CarboItaly, CarboMont, ChinaFlux, Fluxnet-Canada, GreenGrass, ICOS, KoFlux, LBA, NECC, OzFlux-TERN, TCOS-Siberia, and USCCC. The ERA-Interim reanalysis data are provided by ECMWF and processed by LSCE. The FLUXNET eddy covariance data processing and harmonization was carried out by the European Fluxes Database Cluster, AmeriFlux Management Project, and Fluxdata project of FLUXNET, with the support of CDIAC and ICOS Ecosystem Thematic Center, and the OzFlux, ChinaFlux and AsiaFlux offices.\\
  \medskip
  This material is based upon work supported by the National Science Foundation Graduate Research Fellowship under Grant No. DGE 16-44869. Any opinion, findings, and conclusions or recommendations expressed in this material are those of the authors(s) and do not necessarily reflect the views of the National Science Foundation.
\end{frame}

\begin{frame}{References}
  \begin{enumerate}
  \item Franks, P. J., Berry, J. A., Lombardozzi, D. L., \& Bonan, G. B. (2017). Stomatal function across temporal and spatial scales: deep-time trends, land-atmosphere coupling and global models. \textit{Plant Physiology}, 174(2), 583-602.
    \item Lin, Y. S., Medlyn, B. E., Duursma, R. A., Prentice, I. C., Wang, H., Baig, S., ... \& De Beeck, M. O. (2015). Optimal stomatal behaviour around the world. Nature Climate Change, 5(5), 459-464.
    \item Medlyn, B. E., Duursma, R. A., Eamus, D., Ellsworth, D. S., Prentice, I. C., Barton, C. V., ... \& Wingate, L. (2011). Reconciling the optimal and empirical approaches to modelling stomatal conductance. \textit{Global Change Biology}, 17(6), 2134-2144.
    \item Zhou, S., Yu, B., Huang, Y., \& Wang, G. (2015). Daily underlying water use efficiency for AmeriFlux sites. \textit{Journal of Geophysical Research: Biogeosciences}, 120(5), 887-902.
    \end{enumerate}
\end{frame}

@@

\begin{frame}{ideas}
  full summary statistics
  variance statistics
  joint distributions of LAI and VPD, and RH and esat
  aerodynamic scaling theory.
\end{frame}
